Evaluating infectious disease forecasts with allocation scoring rules

### 2023-03-28 alloscore_manuscript/allocation.rmd

@@

\section{Applications}

\subsection{Application with a quantile elicitation problem}

Consider one of the following problems?
\begin{itemize}
\item "should we expand hospital bed capacity"
\item "should impose a stay at home order".
\end{itemize}
for individual locations with specific costs for taking the action and possible costs for "under-acting". Both are I think hard to operationalize in the sense that it's not immediate what specifically those costs should be.

\subsection{Application with an allocation problem}

Hospital admissions in the U.S.

>>>>

Note: it may make sense to talk about less theory in this article?

@@

\section{Application}

We illustrate with an application to hospital admissions in the U.S., considering the problem of allocation of a limited supply of medical resources to the states.
